### 2018-03-04 interfer/paper.tex
Fabry measurements

\input{header}
\usepackage{tikz}
\usetikzlibrary{optics}

\physics
\begin{document}
\papertitle{Interferometers}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{}
\begin{paperabs}

@@

	Interference patterns produced by various light sources may be studied using interferometers, which operate by dividing either the wavefront or the amplitude of the original light beam. In this experiment, an amplitude-splitting interferometer, the Michelson interferometer, was used extensively to determine the indexes of refraction of a transparent solid and a gas after being calibrated using a sodium light.

	\paperfig{MichelsonInterferometer}{% Still need to figure out labels (esp. the slide location)
	\begin{tikzpicture}[use optics]
		\node[thick optics element] at (-2.5, 0) {};
		\node[thick optics element, rotate = -45] at (0, 0) {};
		\node[generic optics io, io body aspect ratio = 1] at (-4.0, 0) {};
		\node[mirror] at (3.0, 0) {};
		\node[mirror, rotate = 90] at (0, 3.0) {};
		\node[thick optics element, rotate = -45] at (1.5, -0.5) {};
		\draw[->-] (-3.38, 0) -- (-0.15, 0);
		\draw[->-] (-0.15, 0) -- (-0.15, 3.0);
		\draw[->-] (0, 3.0) -- (0, 0.15);
		\draw[] (0, 0.15) -- (0.15, 0);
		\draw[->-] (0.15, 0) -- (0.15, -3.0);
		\draw[] (-0.15, 0) -- (0, -0.15);
		\draw[->-] (0, -0.15) -- (1.7, -0.15);
		\draw[] (1.7, -0.15) -- (1.85, -0.3);
		\draw[->-] (1.85, -0.3) -- (3.0, -0.3);
		\draw[->-] (3.0, -0.45) -- (1.70, -0.45);
		\draw[] (1.70, -0.45) -- (1.55, -0.3);
		\draw[->-] (1.55, -0.3) -- (-0.15, -0.3);
		\draw[->-] (-0.15, -0.3) -- (-0.15, -3.0);
		\node[sensor line, rotate = -90] at (0, -3.2) {};	% May switch this to another element
		\node[thin optics element, rotate = 90] at (0, 2.25) {};
	\end{tikzpicture}}{Schematic diagram of the Michelson interferometer.}

>>>>

\input{header}
\physics
\begin{document}
\papertitle{Interferometers}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{}
\begin{paperabs}

@@

	Interference patterns produced by various light sources may be studied using interferometers, which operate by dividing either the wavefront or the amplitude of the original light beam. In this experiment, the Michelson interferometer was used extensively to determine the indexes of refraction of a transparent solid and a gas after being calibrated using a sodium light. As seen from the schematic below, the Michelson interferometer operates by splitting the amplitude of the incident beam.

	\paperfig{MichelsonInterferometer}{% Still need to figure out labels (esp. the slide location)
	\begin{tikzpicture}[use optics]
		\node[thick optics element] at (-2.5, 0) {};
		\node[thick optics element, rotate = -45] at (0, 0) {};
		\node[generic optics io, io body aspect ratio = 1] at (-4.0, 0) {};
		\node[mirror] at (3.0, 0) {};
		\node[mirror, rotate = 90] at (0, 3.0) {};
		\node[thick optics element, rotate = -45] at (1.5, -0.5) {};
		\draw[->-] (-3.38, 0) -- (-0.15, 0);
		\draw[->-] (-0.15, 0) -- (-0.15, 3.0);
		\draw[->-] (0, 3.0) -- (0, 0.15);
		\draw[] (0, 0.15) -- (0.15, 0);
		\draw[->-] (0.15, 0) -- (0.15, -3.0);
		\draw[] (-0.15, 0) -- (0, -0.15);
		\draw[->-] (0, -0.15) -- (1.7, -0.15);
		\draw[] (1.7, -0.15) -- (1.85, -0.3);
		\draw[->-] (1.85, -0.3) -- (3.0, -0.3);
		\draw[->-] (3.0, -0.45) -- (1.70, -0.45);
		\draw[] (1.70, -0.45) -- (1.55, -0.3);
		\draw[->-] (1.55, -0.3) -- (-0.15, -0.3);
		\draw[->-] (-0.15, -0.3) -- (-0.15, -3.0);
		\node[thin optics element, rotate = -90] at (0, -3.0) {};
		\node[thin optics element, rotate = 90] at (0, 2.25) {};
	\end{tikzpicture}}{\textbf{TODO}}
